### 2022-10-04 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@cf472ac989d9ea38d7b0478bf6f18ab7ef8564f8 🚀

The popularity of graph embedding techniques in machine learning is more
than the search for structural invariants: graphs are discrete objects,
and machine learning techniques tend to handle continuous data better.
Bringing a sparse graph into a continuous, dense vector space (Xu, 2021)
opens up a broader variety of predictive algorithms, notably of the sort
that are able to predict events as probabilities (Murphy, 2022).
Furthermore, the projection of the graph itself is a representation that
can be learned; Runghen et al. (2021), for example, used a neural
network to learn the embedding of a network in which not all
interactions were known, based on the nodes' metadata. This example has
many parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in
which node metadata can be represented by phylogeny, abundance, or
functional traits. Using phylogeny as a source of information assumes
(or strives to capture) the action of evolutionary processes on network
structure, which at least for food webs have been well documented (Dalla
Riva \& Stouffer, 2016; Stouffer et al., 2012; Stouffer et al., 2007);
similarly, the use of functional traits assumes that interactions can be
infered from the knowledge of trait-matching rules, which is similarly
well supported in the empirical literature (Bartomeus, 2013; Bartomeus
et al., 2016; Gravel et al., 2013). Relating this information to an
embedding rather than a list of networks measures would allow to capture
their effect on the more fundamental aspects of network structure;
conversely, the absence of a phylogenetic or functional signal may
suggest that evolutionary/trait processes are not strong drivers of
network structure, therefore opening a new way to perform hypothesis
testing.

>>>>

The popularity of graph embedding techniques in machine learning is more
than the search for structural invariants: graphs are discrete objects,
and machine learning techniques tend to handle continuous data better.
Bringing a sparse graph into a continuous, dense vector space (Xu, 2021)
opens up a broader variety of predictive algorithms, notably of the sort
that are able to predict events as probabilities (Murphy, 2022).
Furthermore, the projection of the graph itself is a representation that
can be learned; Runghen et al. (2021), for example, used a neural
network to learn the embedding of a network in which not all
interactions were known, based on the nodes' metadata. This example has
many parallels in ecology (see fig.~\ref{fig:embedding} \textbf{C}), in
which node metadata can be represented by phylogeny, abundance, or
functional traits. Using phylogeny as a source of information assumes
(or strives to capture) the action of evolutionary processes on network
structure, which at least for food webs have been well documented (Dalla
Riva \& Stouffer, 2016; Stouffer et al., 2012; Stouffer et al., 2007);
similarly, the use of functional traits assumes that interactions can be
inferred from the knowledge of trait-matching rules, which is similarly
well supported in the empirical literature (Bartomeus, 2013; Bartomeus
et al., 2016; Gravel et al., 2013). Relating this information to an
embedding rather than a list of networks measures would allow to capture
their effect on the more fundamental aspects of network structure;
conversely, the absence of a phylogenetic or functional signal may
suggest that evolutionary/trait processes are not strong drivers of
network structure, therefore opening a new way to perform hypothesis
testing.
